Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-09-17 paper/paper.tex
Made edits to viral rescue for variants of interest (non SNP). Will keep working on any outstanding methods and next set of figures

We used these constructs to generate lentiviral vectors~\citep{oconnell2010lentiviral} which were used to transduce of A549 cells in the presence of 5 $\mu$g polybrene.
We then sorted single transduced cells and expanded them.
A portion of the expanded cells were tested for reporter activity by transfecting poly(I:C) (a potent agonist of the RIG-I pathway), and we retained clones with strong activation.
Importantly, the cells that we retained for further use were not the same portion that were tested by poly(I:C) treatment, but rather a separate split of the same population---this avoids any selection on the cells from transient activation of IFN.
For the dual type I / type III reporter used in \FIGSUPP[IFNrare]{type_I_vs_III}, a single-cell clone of the type III reporter cell line was transduced with the type I reporter bearing the mCherry fluorescent marker, and then isolated and propagated as a single cell clone for the other cell lines.

@@

\subsection{Viruses for validation experiments}
\jdbcomment{Alistair writes this. I've copied text from prior consolidated section, but it needs to be clarified by more clearly breaking things down by virus.}
All viruses were generated using reverse-genetics as previously described.
All infections were performed in influenza growth media as previously described.
Briefly, bidirectional plasmids producing viral mRNA and vRNA are transfected into a co-culture of MDCK-SIAT1 and 293t cells grown in D10.
After 24h, media is changed from D10 to influenza growth media.
Between 48h and 72h post-infection, depending on viral growth kinetics, supernatant was harvested and titered by TCID50.
Virus was subsequently expanded on MDCK-SIAT1 cells as described below.
For all viral variants, the described mutations were introduced into reverse-genetics plasmids using PCR mutagenesis. 
For the HA-flanked mCherry pseudovirus, a plasmid was generated similarly to a previously-described HA-flanked eGFP vector.
Synonymously-barcoded virus utilized previously described 3' synonymous mutations, and two newly-introduced single-nucleotide synonymous mutations at the 5' end of each viral gene.
Wild-type, synonymously-barcoded, NS1-inactivated, and single-nucleotide variant viruses were all grown in unmodified MDCK-SIAT1 and 293t cells.
Viral variants bearing large internal deleltions in the PB1 segment were grown in MDCK-SIAT1 and 293t cells expressing PB1 as previously described.
Pseudovirus expressing mCherry in place of eGFP was grown in MDCK-SIAT1 and 293t cells expressing HA as previously described.

Wildtype and synonymously barcoded viruses in \FIGDATA[workflow]{virus_seqs} obtained from reverse-genetic transfections was subsequently propagated at an MOI of 0.001 for 72h twice in MDCK-SIAT1 cells (wild-type) or once at an MOI of 0.01 (barcoded) for 60h in order to generate potential immunostimulatory diversity.
For analyses of interferon induction, an additional wild-type stock of virus was grown at an MOI of 0.01 for 36h in order to generate a population relatively free of defective particles. (WILL REPEAT WITH 48H STOCK AS DESCRIBED BELOW)
Viruses bearing SNPs, deletions in PB1, NS1-inactivation mutations, and HA-mCherry pseudovirus were all propagated at an MOI of 0.01 for 48h owing to slower growth kinetics. 
All stocks were subsequently titered by TCID50, using complementing cells where necessary.
Additionally, for qPCR experiments, stocks were titered by qPCR against the viral HA segment using a plasmid standard to determine relative genome copy numbers between viral stocks.

@@

>>>>

We used these constructs to generate lentiviral vectors~\citep{oconnell2010lentiviral} which were used to transduce of A549 cells in the presence of 5 $\mu$g polybrene.
We then sorted single transduced cells and expanded them.
A portion of the expanded cells were tested for reporter activity by transfecting poly(I:C) (a potent agonist of the RIG-I pathway), and we retained clones with strong activation.
Importantly, the cells that we retained for further use were not the same portion that were tested by poly(I:C) treatment, but rather a separate split of the same population---this avoids any selection on the cells from transient activation of IFN.
For the dual type I / type III reporter used in \FIGSUPP[IFNrare]{type_I_vs_III}, a single-cell clone of the type III reporter cell line was transduced with the type I reporter bearing the mCherry fluorescent marker, and then isolated and propagated as a single cell clone for the other cell lines.
All reporter lines tested negative for mycoplasma contamination by the Fred Hutch Genomics Core.

@@

\subsection{Viruses for validation experiments}
\jdbcomment{Alistair writes this. I've copied text from prior consolidated section, but it needs to be clarified by more clearly breaking things down by virus.}

All viruses were generated using reverse-genetics as previously described using plasmids derived from pHW181-PB2, pHW182-PB1, pHW183-PA, pHW184-HA, pHW185-NP, pHW186-NA, pHW187-M, and pHW188-NS~\citep{hoffmann2000dna}.
To generate viruses from these plasmids, or variants described below, we transfected an equimolar mix of all eight plasmids into cocultures of 293T and MDCK-SIAT1 cells seeded at a ratio of 8:1. At 24 hr post-transfection, we changed media from D10 to influenza growth media (Opti-MEM supplemented with 0.01\% heat-inactivated FBS, 0.3\% BSA, 100 U of penicillin/ml, 100 $\mu$g of streptomycin/ml, and 100 $\mu$g of calcium chloride/ml). At 48-72h post-transfection we harvested the virus-containing supernatant, pelletted cellular material by centrifugation at 300 x g's for 4 min, and stored aliquots of the clarified viral supernatant at 80$^{\circ}$C.
We then titered thawed aliquots of viral by TCID50 on MDCK-SIAT1 cells, computing titers via the formula of Reed and Muench as described above.

For comparisons of interferon stimulation a relatively pure stock of WSN influenza was derived by harvesting reverse-genetics supernatants at 48h post infection and passaging virus on MDCK-SIAT1 cells for 36h at an MOI of 0.05---conditions which we previously validated to lead to stocks relatively depleted in defective particles~\citep{russell2018extreme}.

To generate an NS1-inactivated strain of influenza, six nucleotide changes resulting in the addition of five in-frame stop codons introduced immediately downstream of the 5' splice donor site, interrupting translation of NS1 while leaving NS2 (NEP) intact.
The viral RNA produced by this vector is described in (sequence)\abrcomment{I have uploaded the genbank files, just waiting for appropriate figure to append}.
This modified plasmid was used in a reverse-genetics approach to recapitulate mutant virus, harvesting transfection supernatant after 72h.
This virus was then passaged in MDCK-SIAT1 cells for 48h at an MOI of 0.05---due to slower growth kinetics than the wild-type virus this longer incubation was necessary.
Genome copy number of this virus relative to infectious titer was determined as described below by qPCR.

To generate viruses bearing internal deletions in the PB1 segment, indicated regions of the PB1 segment were excised by PCR from our reverse genetics plasmids.
Sequences are described in (sequence) \abrcomment{I have uploaded the genbank files and modified coordinates in map names to match mRNA coordinates, just waiting for appropriate figure to append}. 
To rescue these viruses, we used 293t cells and MDCK-SIAT1 cells transduced to constituitively express PB1 as previously described!\citep{Bloom2010oseltamivir}. 
Virus was harvested from transfections at 72h, and passaged twice in MDCK-SIAT1 cells expressing PB1 constituitively at an MOI of 0.001 for 72h and 0.01 for 48h. 
This passaging was necessary as viral titers from transfections were too low to generate sufficient virus from a single passage.
This virus was titered on complementing MDCK-SIAT1 cells.
Genome copy number of this virus relative to infectious titer was determined as described below by qPCR.

To generate pseudovirus that expresses fluorescent mCherry instead of HA, a plasmid was generated similarly to a previously-described eGFP-expressing pseudovirus~\citep{russell2018extreme}. 
To rescue this virus, we used MDCK-SIAT1 cells transduced to constituitively express HA and included an HA protein expression plasmid in our reverse-genetics transfection mixture.
Virus was harvested from transfections at 72h and passaged for 48 at an MOI of 0.01 on MDCK-SIAT1 cells that express HA. 
This virus was titered on complementing MDCK-SIAT1 cells.

@@

\end{document}
ent}
_figures/pacbio_analysis.html}.
This notebook contains detailed descriptions of each step and plots illustrating the results, and is the best way to understand this part of the analysis in detail.
The actual Jupyter notebook rendered here is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb.}}
\end{suppfile}

\end{document}
ent}
mlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb.}}
\end{suppfile}
